---
title: "Video Game Sales"
author: "Dhileas Heywood"
date: "27/05/2020"
output:
  powerpoint_presentation: default
  slidy_presentation: default
  beamer_presentation: default
---

```{r, include=FALSE}
library(tidyverse)
library(knitr)
sales_global <- read_csv("../clean_data/sales_global.csv")
sales_north_america <- read_csv("../clean_data/sales_north_america.csv")
sales_europe <- read_csv("../clean_data/sales_europe.csv")
sales_japan <- read_csv("../clean_data/sales_japan.csv")
sales_other <- read_csv("../clean_data/sales_other.csv")
sales_all_regions <- read_csv("../clean_data/sales_all_regions.csv")
```





```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Project Brief

* To understand what types of games sell a lot of copies 
* In particular, analysis to help make a decision on which direction to take the company

## What Genre of Games Sells the Most Copies?
```{r}
sales_global %>% 
  filter(year > 1999) %>% 
  #filter(!str_detect(name, "[Mm]inecraft")) %>% 
  group_by(genre) %>% 
  summarise(median_global_sales = median(global_sales), number_games = length(unique(name))) %>% 
  ggplot(aes(x = genre, y = median_global_sales)) +
  geom_col() +
  labs(x = "Genre",
       y = "Mean Global Sales (Millions)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) #+
  #scale_fill_viridis_b() +
  #ylim(0, 0.7)
```


## But How Many Games are in Each Category?

```{r, echo = FALSE}
sales_global %>% 
  filter(year > 1999) %>% 
  group_by(genre) %>% 
  summarise(`Median Global Sales` = median(global_sales), `Number of Games` = length(unique(name))) %>% 
  arrange(`Number of Games`) %>% 
  head(12) %>% 
  kable()
```

## Corrected to Compensate for Minecraft
```{r echo=FALSE, fig.height=7.5, fig.width=10}
sales_global %>% 
  filter(year > 1999) %>% 
  group_by(genre) %>% 
  summarise(median_global_sales = median(global_sales), number_games = length(unique(name))) %>% 
  filter(number_games >= 10) %>% 
  ggplot(aes(x = genre, y = median_global_sales)) +
  geom_col() +
  labs(x = "Genre",
       y = "Mean Global Sales (Millions)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_label(aes(label = number_games), vjust = 1.2) 
```

## What About Seperate Markets?
```{r fig.height=7.5, fig.width=10}
sales_all_regions %>% 
  filter(year > 1999) %>% 
  group_by(genre, region) %>% 
  summarise(median_sales = median(regional_sales), number_games = length(unique(name))) %>% 
  filter(number_games >= 10) %>% 
  ggplot(aes(x = genre, y = median_sales, fill = number_games)) +
  geom_col() +
  labs(x = "Genre",
       y = "Mean Global Sales (Millions)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_viridis_b()+
  #geom_label(aes(label = number_games), vjust = 1) +
  facet_wrap(~ region, scales = "fixed")
  
  
```


## The Global Markets

```{r echo=FALSE, message=FALSE, warning=FALSE}
sales_all_regions %>% 
  ggplot(aes(x = global_sales, y = regional_sales)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Global Sales") +
  ylab("Regional Sales") +
  facet_wrap(~ region) +
  scale_colour_viridis_d(option = "viridis")
```

## How do Sales Compare With Rating?

```{r}
sales_all_regions %>% 
  filter(year > 1999, region == "europe" | region == "north america") %>% 
  group_by(esrb_rating, region) %>% 
  summarise(median_sales = median(regional_sales), number_games = length(unique(name))) %>% 
  ggplot(aes(x = esrb_rating, y = median_sales)) +
  geom_col() +
  labs(x = "ESRB Rating",
       y = "Mean Sales (Millions)") +
  facet_wrap(~ region) +
  geom_label(aes(label = number_games), vjust = 1.2) 
```

## How Do Sales Differ for Different Platforms?

```{r}
sales_na_eu <- left_join(sales_north_america, sales_europe, by = c("name", "basename", "genre", "esrb_rating", "platform", "publisher", "developer", "year", "rank")) %>% 
  pivot_longer(cols = c("na_sales", "pal_sales"), names_to = "region", values_to = "sales") %>% 
  separate(col = region, into = c("region", "rubbish"), sep = "_") %>% 
  select(-rubbish) %>% 
  mutate(region = ifelse(region == "pal", "europe", "north america")) %>% 
  drop_na()
  
sales_na_eu %>% 
  group_by(platform, region) %>% 
  summarise(median_sales = median(sales), number_games = length(unique(name))) %>% 
  ggplot(aes(x = platform, y = median_sales)) +
  geom_col() +
  scale_fill_viridis_c() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ region) +
  geom_label(aes(label = number_games), vjust = 1.2) 
```

## When This is Put Together
```{r}
sales_na_eu %>% 
  filter(genre == "Shooter" | genre == "Racing" | genre == "Sports" | genre == "Action" | genre == "Action-Adventure" | genre == "Platform",
         esrb_rating == "M" | esrb_rating == "E" | esrb_rating == "T") %>% 
  group_by(platform, region, genre, esrb_rating) %>% 
  summarise(median_sales = median(sales), number_games = length(unique(name))) %>% 
  ggplot(aes(x = platform, y = median_sales, fill = genre)) +
  geom_col() +
  scale_fill_viridis_d() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(esrb_rating ~ region, ncol = 2) #+
  #geom_label(aes(label = number_games), vjust = 1.2)  
```

## In Conclusion

* Games with an ESRB rating of "Mature" sell more games on average
* Games released on XBox and PlayStation sell well in Europe and North America
\t* Games released on PC do better in Europe
\t* Games released on Nintendo do better in North America
* Games in the Shooter, Platform and Action/Action-Adventure genres sell well. 

## Any Questions?